\documentclass{article}
\usepackage{scimisc-cv}
\usepackage{hyperref}
\usepackage[utf8]{inputenc}

\title{Resume}
\author{Jerry Mao}
\date{Mar. 2025}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue
}

%% These are custom commands defined in scimisc-cv.sty
\cvname{Jerry (Chen-Nien) Mao}
\cvpersonalinfo{
Lead Software Engineer with Yahoo! \cvinfosep 
\href{mailto:chennien.mao@gmail.com}{chennien.mao@gmail.com} \cvinfosep
\href{https://www.linkedin.com/in/chennien-mao/}{LinkedIn:chennien-mao}
\cvinfosep Taipei, Taiwan
}

\begin{document}

\makecvtitle %% This is a custom command constructing the CV title from \cvname, \cvpersonalinfo

\section{Experience}

\cvsubsection{Lead Software Engineer}[Oct. 2022 to present]
[Yahoo! Inc.][Taipei, Taiwan]
\begin{itemize}
	\item \textbf{Yahoo Knowledge, Global Search} (Java, Spark, GraphQL, AWS) 
		\begin{itemize}
			\item Led a team of 4 engineers to develop and maintain TB-scale data pipelines for Yahoo's largest knowledge graph, enhancing global search experience and powering content semantic services across Yahoo products.
			\item Designed and architected an LLM application using RAG to provide trustworthy answers for the search autocomplete service.
			\item Directed the AWS migration to modernize the tech stack, executing a multi-stage migration plan to ensure seamless traffic transition with zero downtime for internal and cross-functional teams.
			\item Led and transitioned project responsibilities from a 20+ member US team to Taiwan, ensuring uninterrupted operations and high data quality.
		\end{itemize}
	\item \textbf{News \& Trending, Global Search} (Java, Spring Webflux, Vespa, Pulsar, AWS) 
		\begin{itemize}
			\item Acted as the \textbf{architect role in the product squad}, collaborating with internal and external teams across different time zones to achieve business requirements across Yahoo and its business partners' product lines.
			\item Served as the \textbf{project owner for the News and Trending platforms}, leading and mentoring a team of 6 engineers. Facilitated sprint agile ceremonies and hosted engineering sharing sessions within the team to foster growth and collaboration.
			\item Directed an API modernization project that migrated a legacy API to a modern framework. Comprehensive testing minimized revenue risk while reducing p99 latency by 54\%, system resource usage by 53\%, and CI/CD deployment time by 60\%.
			\item Collaborated with scientists to deliver personalized trending content based on user footprints, boosting module traffic by 14\%. Worked with cross-functional teams to extend the feature to the Yahoo homepage, increasing US search volume by 2\%.
			\item Designed and executed the migration of a serving layer handling 600K QPS from bare-metal infrastructure to AWS, ensuring seamless data service transitions while maintaining consistency throughout the migration.
		\end{itemize}
	\item \textbf{Gemini, Global Ads} (Java, Spring Webflux, AWS) 
		\begin{itemize}
			\item Contributed to the Yahoo Native Ads serving platform by refactoring a revenue-sensitive API from C++ to Java on AWS EKS, maintaining performance and revenue for an Ads feedback API handling 70K QPS globally.
		\end{itemize}
\end{itemize}

\cvsubsection{Backend Engineer}[Sep. 2021 to Oct. 2022]
[Shopee][Singapore]
\begin{itemize}
	\item \textbf{Promotion Service} (Go, Python, Django)
		Shopee is a leading e-commerce platform in Southeast Asia.
		Developed and maintained the Promotion API and admin services supporting price discounts and coupon distribution at 100K+ QPS. 
		Collaborated with diverse engineer teams to consolidate pricing and shipping discount logic into an unified data gateway for promotion microservices.
\end{itemize}

\cvsubsection{Senior Software Engineer}[Oct. 2019 to Sep. 2021]
\cvsubsection{Software Engineer}[Aug. 2017 to Oct. 2019]
[Yahoo!][Taipei, Taiwan]
\begin{itemize}
	\item \textbf{Search Platform, Global Search} (Go, Python, Django) 
	Developed and maintained various high-impact search services, including TrendingNow, TV Series Search for Taiwan, and Real-time Local Search. Key achievements: 
	\begin{itemize}
		\item  Contributed a automated data pipeline for discovering high-revenue trending terms to increase the module revenue by 70\%, 
		\item  Built a TV guide module covering 1\% of Taiwan search traffic with a 25\% click rate, 
		\item  Designed real-time data pipelines for public bike rental service in Taiwan and supporting mask inventory search during pandemic, awarded \textbf{Best Poster} at Yahoo Tech conference, 2020.
	\end{itemize}
\end{itemize}

% \cvsubsection{Software Engineer}[Aug. 2017 to Oct. 2019]
% [Yahoo!][Taipei, Taiwan]
% \begin{itemize}
% 	\item \textbf{Dictionary Search} (Java, Python) Project owner of Yahoo Dictionary. Delivered a redesign for Taiwan and Hong Kong markets, increasing daily active users by 12\%. Maintained the back-end system supporting global dictionary search scenarios across Yahoo products.
% 	\item \textbf{Yahoo Search} (Front-end) Contributed to various Yahoo search interface developments. Key achievements: 1) Implemented image ads, increasing revenue by 2\% in Taiwan, 2) Optimized local search with Ajax, boosting user clicks by 1\%, 3) Consolidated carousel implementations, reducing complexity and maintenance effort.
% \end{itemize}
% \cvsubsection{Research Assistant}[Nov. 2014 to Jun. 2017]
% [Networking and Multimedia Systems Lab (NMSL), National Tsing Hua University][Hsinchu, Taiwan]
% \begin{itemize}
% \item I have been with NMSL since my senior year as a research assistant and contributed to several projects. \begin{itemize}
% % \item \textbf{5G Cloud} (Advisors: Dr. Cheng-Hsin Hsu and Dr. Yeh-Chin Chung):  I studied and deployed an opensource project, Open Air Interface, which implements the Radio Access Networks in software. We virtualize the Radio Access Networks in the cloud ushttps://www.overleaf.com/project/5efdfc7bd82afb000103a715ing the Docker containers and Kubernetes.
% \item \textbf{5G Cloud} (Advisors:  Dr. Cheng-Hsin Hsu and Dr. Yeh-Chin Chung): I studied and deployed an opensource project, Open Air Interface, which implements the Radio Access Networks in software. We virtualize the Radio Access Networks with containers and use Kubernetes for deployment.

% \end{itemize}
% \end{itemize}

%\cvsubsection{Research Intern}[Aug. 2015]
%[Wireless and Mobile Communication Technology R\&D Center, TsingHua University][Beijing, China]
%\begin{itemize}
%\item I participated in the 5G project, which is a joint project between National Tsing Hua University, Hsinchu, and TsingHua University, Beijing. I was invited by TsingHua
%University to share the experience on 5G virtualization.
%\end{itemize}

\section{Education}
\cvsubsection{M.S., Department of Computer Science, National Tsing Hua University}[Hsinchu, Taiwan]
[Networking and Multimedia Systems Lab][Sept 2015 to Jun 2017]

% \begin{itemize}
% 	\item Research Fields: Computer Networks, Radio Access Networks, Cloud, Software Defined Networks
% 	\item GPA 4.16/4.3
% 	      \item Publication
% 	      \begin{itemize}
% 	      \item \textbf{Chen-Nien Mao}, Mu-Han Huang, Satyajit Padhy, et al., "Minimizing Latency of Real-Time Container Cloud for Software Radio Access Networks.", in Proc. of IEEE 7th International Conference on Cloud Computing Technology and Science, 2015 
% 	      \item Mu-Han Huang, Yu-Cing Luo and \textbf{Chen-Nien Mao}, et al., "Performance evaluations of cloud radio access networks." in Proc. of 12th EAI International Conference on Heterogeneous Networking for Quality, Reliability, Security and Robustness, 2016
% 	      \end{itemize}
% \end{itemize}

\cvsubsection{B.S., Department of Computer Science, National Tsing Hua University}[Hsinchu, Taiwan]
[Computer Science][Sept 2011 to Jun 2015]
% \begin{itemize}
% 	\item GPA 3.77/4.3 (3.9 for Computer Science Courses)
% \end{itemize}

% \section{Publication}
% \begin{itemize}
% \item  \textbf{Chen-Nien Mao}, Mu-Han Huang, Satyajit Padhy, et al., "Minimizing Latency of Real-Time Container Cloud for Software Radio Access Networks.", in Proc. of IEEE 7th International Conference on Cloud Computing Technology and Science,
% 2015  
% % 
% \end{itemize}

\section{Skills}
\begin{description}[widest=Langauges]
	\item[Programming Skills:]
		\textbf{Python}, Java, Scala, and Go
	\item[Cloud \& Infrastructure:]
		\textbf{AWS}, Kubernetes, Docker, Terraform
	\item[Technical stack:]
	    Spring Webflux, Django, Vespa, Pulsar, Kafka, PySpark
	\item[Monitoring \& Observability:]
		OpenTelemetry, Prometheus, Grafana, Splunk
	\item[Languages:]
		\textbf{English} (Professional Proficiency), \textbf{Mandarin} (Native)
\end{description}


\end{document}
